---
title: "Practical Machine Learning Project"
author: "Borg"
date: "2016年4月23日"
output: html_document
---
# Overview  
Use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants to predict which activity they were performing. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. 

# Data  
The training data for this project are available [here](https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv)  
The test data are available [here](https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv)  
The data for this project come from this source: <http://groupware.les.inf.puc-rio.br/har>.   
More information is available from the website here: [Human Activity Recognition](http://groupware.les.inf.puc-rio.br/har) (see the section on the Weight Lifting Exercise Dataset). 

# Loading Data and Library
Download traning data and testing data into working directory and load data.
```{r}
library(dplyr)
library(caret)
library(rpart)
training <- read.csv("pml-training.csv")
testing <- read.csv("pml-testing.csv")
dim(training)
dim(testing)
```
The training dataset should have 19622 rows and 160 columns.

# Feature Selection
Select most useful features.
```{r}
names<-names(training)
features <- names[grepl("^roll|^pitch|^yaw|^gyros|^accel|^magnet.*",names)]
training_feature <- training[,c(features,"classe")]
```

# Exploratory Data Analysis & Base-line Accuracy
```{r}
summary(training_feature$classe)
baseline <- summary(training_feature$classe)[1]/nrow(training_feature)
```
Our traning data contains 5 classes. Our model accuracy should be larger than `r baseline`, which is accuracy of predictiong the majority class all the time.

# Train Models Using Cross Validation
Train lda and rpart model.
```{r cache=TRUE,results='hide'}
set.seed(123)
tc <- trainControl("cv",10)
ldamodel <- train(classe~.,method="lda",trControl=tc,data=training_feature)
rpartmodel <- train(classe~.,method="rpart",trControl=tc,data=training_feature)
```

Stack three models together.
```{r cache=TRUE,results='hide'}
lda_est <- predict(ldamodel,training_feature)
rpart_est <- predict(rpartmodel,training_feature)
ests <- data.frame(lda_est=lda_est,rpart_est=rpart_est,classe=training_feature$classe)
combine_model <- train(classe~.,method="rpart",data=ests)
```

# Model Evaluation
Evaluation on training data. Since my laptop is rusty, I am not running gbm or rf model.  
```{r}
combine_est <- predict(combine_model,ests)
confusionMatrix(lda_est,training_feature$classe)$overall["Accuracy"]
confusionMatrix(rpart_est,training_feature$classe)$overall["Accuracy"]
confusionMatrix(combine_est,training_feature$classe)$overall["Accuracy"]
```  
On training data, lda model is the best fit. Combining lda and rpart model with rpart model reduce accuracy compared with lda only. Thus we'll be using lda as the final model.

# Plot lda_est against classe
```{r}
qplot(x=training_feature$classe,y=lda_est)+geom_jitter()
```  
As shown in the plot, the model's performance is rather good. Density of points around the diagnoal(classe==lda_est) is higher.

# Using lda Model to Predict
```{r}
testing_feature <- testing[,c(features)]
lda_est_test <- predict(ldamodel,testing_feature)
lda_est_test
summary(lda_est_test)
```  