---
title: "Practical Machine Learning Project"
author: "Borg"
date: "2016年4月23日"
output: html_document
---
# Overview  
Use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants to predict which activity they were performing. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. 

# Data  
The training data for this project is available [here](https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv)  
The test data is available [here](https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv)  
The data for this project comes from the source: <http://groupware.les.inf.puc-rio.br/har>.   
More information is available from the website here: [Human Activity Recognition](http://groupware.les.inf.puc-rio.br/har) (see the section on the Weight Lifting Exercise Dataset). 

# Loading Data and Library
Download traning data and testing data into working directory and load data.
```{r}
library(dplyr)
library(caret)
library(rpart)
training <- read.csv("pml-training.csv")
testing <- read.csv("pml-testing.csv")
dim(training)
dim(testing)
```
The training dataset should have 19622 rows and 160 columns.

# Feature Selection
Select most useful features.
```{r}
names<-names(training)
features <- names[grepl("^roll|^pitch|^yaw|^gyros|^accel|^magnet.*",names)]
training_feature <- training[,c(features,"classe")]
```

# Exploratory Data Analysis & Base-line Accuracy
```{r}
summary(training_feature$classe)
baseline <- summary(training_feature$classe)[1]/nrow(training_feature)
```
Our traning data contains 5 classes. Our model accuracy should be larger than `r baseline`, which is accuracy of predicting the majority class all the time.

# Train Models Using Cross Validation
Train gbm and rf model.
```{r cache=TRUE,results='hide'}
set.seed(123)
inTrain <- createDataPartition(training_feature$classe,p=0.8,list = FALSE)
train <- training_feature[inTrain,]
validation <- training_feature[-inTrain,]
tc <- trainControl("cv",10)
if(file.exists("gbmmodel.rd")){
  readRDS("gbmmodel.rd")
}else{
  gbmmodel <- train(classe~.,method="gbm",trControl=tc,data=train)
}
if(file.exists("rfmodel.rd")){
  readRDS("rfmodel.rd")
}else{
  rfmodel <- train(classe~.,method="rf",trControl=tc,data=train)
}
```

Combine two models with rf model.
```{r cache=TRUE,results='hide'}
gbm_est <- predict(gbmmodel,train)
rf_est <- predict(rfmodel,train)
if(file.exists("combinemodel.rd")){
  readRDS("combinemodel.rd")
}else{
  ests <- data.frame(gbm_est=gbm_est,rf_est=rf_est,classe=train$classe)
  combine_model <- train(classe~.,method="rf",data=ests)
}
```

# Model Evaluation
Evaluation on validation data.
```{r}
gbm_est <- predict(gbmmodel,validation)
rf_est <- predict(rfmodel,validation)
ests <- data.frame(gbm_est=gbm_est,rf_est=rf_est)
combine_est <- predict(combine_model,ests)
confusionMatrix(gbm_est,validation$classe)$overall["Accuracy"]
confusionMatrix(rf_est,validation$classe)$overall["Accuracy"]
confusionMatrix(combine_est,validation$classe)$overall["Accuracy"]
```  
On validation data, combined model performs equally well as rf model. Choose rf model for the convenience of data preprocessing.

# Variable Importance
```{r}
varImp(rfmodel$finalModel)
```  
Belt matters most!

# Using rf Model to Predict
```{r}
test <- testing[,c(features)]
est_rf_test <- predict(rfmodel,test)
summary(est_rf_test)
```  
